```{r setup, include=FALSE}
current_date <- Sys.Date()
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Week 1 Quiz"
author: "Andy Boettcher"
date: `r current_date`
output: html_document
---

1. The R language is a dialect of which of the following programming languages?
A: S

2. The definition of free software consists of four freedoms (freedoms 0 through 3).  Which of the following is NOT one of the freedoms that are part of the defintion? I answer in the positive.
A: The freedom to study how the program works, and adapt it to your needs.
A: The freedom to redistribute copies to help your neighbor.
A: The freedom to run the program, for any purpose.
A: The freedom to improve the program, and release your improvements to the public, so the whole community benefits.

3. What are the atomic datatypes in R?
A: logical, integer, double, complex, character, raw

4. What is the class of function below?

```{r question4}
x <- 4
class(x)
```

5. What is the class of function below?

```{r question5}
x <- c(4, "a", TRUE)
class(x)
```

6. What is produced by the expression cbind(x,y)?
```{r question6}
x <- c(1,3,5)
y <- c(3,2,10)

cbind(x,y)
```

7. A key property of vectors in R is that
A: elements of a vector all must be of the same class

8. Suppose I have a list defined as x <- list(2,"a","b",TRUE). What does x[[2]] give me? Select all that apply.
```{r question8}
x <- list(2,"a","b",TRUE)
x[[2]]
```

9. Suppose I have a vector x <- 1:4 and a vector y <- 2. What is produced by the expression x + y?
```{r question9}
x <- 1:4
y <- 2
x+y
```

10. Suppose I have a vector x <- c(17,14,4,5,13,12,10) and I want to set all elements of this vector that are greater than 10 to be equal to 4.  What R code achieves this?
```{r question10}
x <- c(17,14,4,5,13,12,10)
x[x > 10] <- 4
print(x)
```

11. Using the week 1 dataset answer the questions 11-20.
```{r question11-20}
week_1 <- read.csv(file = "data/hw1_data.csv", header=TRUE, sep = ",")
colnames(week_1)
head(week_1, n=2)
dim(week_1)
tail(week_1, n=2)
week_1[47,]
summary(week_1)

week_1_sub <- week_1[which(week_1$Ozone > 31 & 
                           week_1$Temp > 90),]
summary(week_1_sub)

week_1_month_sub <- week_1[which(week_1$Month == 6),]
summary(week_1_month_sub)

week_1_month_sub <- week_1[which(week_1$Month == 5),]
summary(week_1_month_sub)

```
